\section{Meromorphic functions and Siegel theorem on function fields}

\subsection{Meromorphic functions}

    \begin{definition}\label{def:meromorphic_functions}
        Let \(M\) be a complex manifold. 
        A \emph{meromorphic function} on \(M\) is a holomorphic map \(f: M \to \bbC\bbP^1\).

        The set of meromorphic functions on \(M\) is denoted by \(\Mer(M)\) or \(\fkk(M)\).
    \end{definition}

    \begin{proposition}\label{prop:meromorphic_functions_and_holomorphic_functions}
        Let \(M\) be a complex manifold. 
        Then there is a natural inclusion \(\Hol(M) \hookrightarrow \Mer(M)\).
        Moreover, we have \(\Mer(M) = \Frac(\Hol(M))\), i.e., every meromorphic function can be expressed as a quotient of two holomorphic functions.
        \Yang{to be checked.}
    \end{proposition}

    \begin{proposition}\label{prop:meromorphic_functions_is_a_field}
        Let \(M\) be a complex manifold. 
        The set of meromorphic functions on \(M\) forms a field under the usual addition and multiplication of functions.
    \end{proposition}

    \Yang{To be complemented and revised.}


\subsection{Siegel theorem}

    \begin{proposition}\label{prop:schwarz_lemma_in_several_variables}
        Let \(f:U \to \bbC\) be a holomorphic function defined on an open subset \(U \subset \bbC^n\).
        Suppose that \(f\) has order \(k\) at a point \(x \in U\).
        Then there exists a neighborhood \(\overline{B(x,r)} \subset U\) of \(x\) such that 
        \[
            |f(z)| \leq C |z - x|^k, \quad \forall z \in \overline{B(x,r)},
        \]
        where \(C = \sup_{z \in \partial \overline{B(x,r)}} \left| f(z) \right|\).
        \Yang{To be revised.}
    \end{proposition}

    \begin{theorem}[Siegel theorem on function fields]\label{thm:Siegel_theorem_on_function_fields_of_complex_manifolds}
        Let \(X\) be a connected and compact complex manifold of dimension \(n\).
        Then the field of meromorphic functions on \(X\) satisfies
        \[
            \trdeg_{\bbC} \fkk(X) \leq n.
        \]
    \end{theorem}
    \begin{proof}
        Let \(\{f_1, f_2, \ldots, f_{n+1}\} \subset \fkk(X)\) be meromorphic functions on \(X\).
        We want to find \(P \in \bbC[x_1, x_2, \ldots, x_{n+1}] \setminus \{0\}\) such that
        \[ P(f_1, f_2, \ldots, f_{n+1}) = 0. \]

        \begin{step}
            Let \(z \in X\), there exists \(g_1, g_2, \ldots, g_{n+1}, h \in \Hol(X)\) such that \(f_i = g_i / h\) for each \(1 \leq i \leq n+1\).
        \end{step}

        \Yang{To be revised and complemented.}
    \end{proof}

    \Yang{To be revised and complemented.}
    